\begin{center}
\begin{landscape}
\footnotesize
\begin{longtable}{@{}lllp{6cm}@{}}
\toprule
Attribute & Level & Reference & Remark\\
\midrule
\endfirsthead
\multicolumn{4}{l}{\tablename\ \thetable\ -- \emph{Continued from previous page}}\\
\toprule
Attribute & Level & Reference & Remark\\
\midrule
\endhead
\midrule
\multicolumn{4}{r}{\emph{Continued on next page}}
\endfoot
\endlastfoot
\emph{Car} &
&
&
\\
\quad Type &
\begin{tabular}[t]{@{}l@{}}Small car\\      Medium to large car\\      Minivan or van\\      SUV\\      Luxury or sports car\end{tabular} &
&
\\
\quad Fuel &
\begin{tabular}[t]{@{}l@{}}Gasoline\\      Diesel\\      Electric\\      Hybrid\\      Plug-in hybrid\end{tabular} &
&
\\
\quad Fixed   cost &
\begin{tabular}[t]{@{}l@{}}0.7 (-30\%)\\      1\\      1.3 (+30\%)\end{tabular} &
Inferred from archetype* &
Fixed costs include   amortization, garaging costs, insurance, and taxes. The price of the car is   reflected in the fixed cost (amortization). \\
\quad Variable   cost &
\begin{tabular}[t]{@{}l@{}}0.7 (-30\%)\\      1\\      1.3 (+30\%)\end{tabular} &
Inferred from archetype* &
Per kilometer cost, including   depreciation of the car's value, fuel or energy costs, tire costs and   maintenance. \\ \midrule
\emph{Public transport} &
&
&
\\
\quad Type &
\begin{tabular}[t]{@{}l@{}}National season ticket   (GA)\\      Regional season ticket\\      Half-fare\end{tabular} &
&
\\
\quad Class &
\begin{tabular}[t]{@{}l@{}}First\\      Second\end{tabular} &
&
Cost multiplier of 1.7 for first   class \\
\quad Fixed   cost &
\begin{tabular}[t]{@{}l@{}}0.7 (-30\%)\\      1\\      1.3 (+30\%)\end{tabular} &
\begin{tabular}[t]{@{}l@{}}3860 CHF/year (GA)\\      782 CHF/year (Regional)\\      185 CHF/year (Half-fare)\end{tabular} &
\\
\quad Additional   zone &
\begin{tabular}[t]{@{}l@{}}0.7 (-30\%)\\      1\\      1.3 (+30\%)\end{tabular} &
40 CHF for additional zone &
Only for regional season ticket \\ \midrule
\emph{Bicycle} &
&
&
\\
\quad Type &
\begin{tabular}[t]{@{}l@{}}Regular bike\\      E-bike (up to 25 km/h)\\      E-bike (up to 45 km/h)\end{tabular} &
&
\\
\quad Fixed   cost &
\begin{tabular}[t]{@{}l@{}}0.7 (-30\%)\\      1\\      1.3 (+30\%)\end{tabular} &
\begin{tabular}[t]{@{}l@{}}200 CHF/year (regular)\\      600 CHF/year (25 km/h)\\      100 CHF/year (45 km/h)\end{tabular} &
Fixed costs include   amortization, maintenance, and insurance. The price of the bicycle is   reflected in the fixed cost (amortization). \\ \midrule
\emph{Car sharing} &
&
&
\\
\quad Free-floating &
\begin{tabular}[t]{@{}l@{}}Yes\\      No\end{tabular} &
&
Whether or not the car sharing   is station-based or free-floating. \\
\quad Membership   fee &
\begin{tabular}[t]{@{}l@{}}10 CHF/month\\      15 CHF/month\\      20 CHF/month\end{tabular} &
&
\\
\quad Time   tariff &
\begin{tabular}[t]{@{}l@{}}2 CHF/h\\      3 CHF/h\\      4 CHF/h\end{tabular} &
&
\\
\quad Km   tariff &
\begin{tabular}[t]{@{}l@{}}0.8 CHF/km\\      1 CHF/km\\      1.2 CHF/km\end{tabular} &
&
\\ \midrule
\emph{Scenario variables} &
&
&
\\
\quad Work   from home &
0-5+ days &
Individual-specific &
Either the current WFH   frequency, the maximum feasible frequency (as asked in the introductory   survey), the free-choice, or the observed choices in the SP. \\
\quad Work   from anywhere &
\begin{tabular}[t]{@{}l@{}}Allowed\\      Not allowed\end{tabular} &
&
\\
\bottomrule
\multicolumn{4}{l}{*An archetype has the average car specifics for a certain car and fuel type combination}\\
\caption{\label{tab:mto-attributes-levels} Attributes and levels of the MTO-SP experiment.}
\end{longtable}
\end{landscape}
\end{center}
